Ancestry linkage in hybrid zones

### 2016-02-10 drafts/hybrid_zone.tex
more text to draft

Of particular interest is whether or targets of selection could potentially be identified by a signal of larger ancestry tracts surrounding them compared to a genome-wide background. To demonstrate this, we simulated a chromosome of length 1M with a selected site at position 0.5M. For a set of positions $\mathbf{m}$ along the chromosome, we computed the length $l_B(m_i)$
of the surrounding unbroken block of ancestry. There is a detectable signal of increased block length surrounding selected loci when conditioning on the less-fit ancestry (Figure~\ref{Fig:blockLengths},~\ref{Supp:blockLengthHeatmap}) at geographic sites far from the center of the zone. A signal is also present, but less well resolved when ancestry is not taken into account (Figures~\ref{Supp:blockLengthHeatmapNoAnc},~\ref{Supp:blockLengthNoAnc}).

\plr{or, perhaps for introduction?}
In addition to our finding that ancestry surrounding selected sites was quite long, our simulations revealed a consistent and unexpected finding. We found, on a given side of the hybrid zone, a transition from the locally adaptive ancestry at the selected site to the alternative ancestry at a closely linked site was short-lived. Put differently, blocks of `wrong' ancestry that do not overlap the selected site but are closely linked are exceptionally short. A simple intuitive explanation for this pattern suggests itself - loci physically linked to the selected sites can only survive on the wrong side of the hybrid zone for a reasonable amount of time if they recombine away from their ancestry at the locally adaptive site. Because it is then tightly linked to the alternate ancestry at the selected site, this ancestry chunk will large recombine with the alternate ancestry, and therefore decay rapidly. This pattern means that we can further refine the signal of block lengths around a selected locus, by measuring the ratio of mean block lengths surrounding a site with the mean length of adjacent blocks (Figures~\ref{Supp:ratioBlockAdjacent},~\ref{Supp:ratioBlockAdjacentHeatmap})

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning}
\caption{Mean block length surrounding positions along a simulated chromosome of length $1M$ with selected locus at position $0.5M$. Here each line represents mean block lengths in a given deme, and is normalized by mean block length along the chromosome in the deme.}\label{Fig:blockLengths}
\end{figure}

>>>>

Of particular interest is whether or targets of selection could potentially be identified by a signal of larger ancestry tracts surrounding them compared to a genome-wide background. To demonstrate this, we simulated a chromosome of length 1M with a selected site at position 0.5M. For a set of positions $\mathbf{m}$ along the chromosome, we computed the length $l_B(m_i)$
of the surrounding unbroken block of ancestry. There is a detectable signal of increased block length surrounding selected loci when conditioning on the less-fit ancestry (Figure~\ref{Fig:blockLengths},~\ref{Supp:blockLengthHeatmap}) at geographic sites far from the center of the zone. A signal is also present for, but less well resolved when ancestry is not taken into account (Figures~\ref{Supp:blockLengthHeatmapNoAnc},~\ref{Supp:blockLengthNoAnc}).

\plr{or, perhaps for introduction?}
In addition to our finding that ancestry surrounding selected sites was quite long, our simulations revealed a consistent and unexpected finding. We found, on a given side of the hybrid zone, a transition from the locally adaptive ancestry at the selected site to the alternative ancestry at a closely linked site was short-lived. Put differently, blocks of `wrong' ancestry that do not overlap the selected site but are closely linked are exceptionally short. A simple intuitive explanation for this pattern suggests itself - loci physically linked to the selected sites can only survive on the wrong side of the hybrid zone for a reasonable amount of time if they recombine away from their ancestry at the locally adaptive site. Because it is then tightly linked to the alternate ancestry at the selected site, this ancestry chunk will large recombine with the alternate ancestry, and therefore decay rapidly. This pattern means that we can further refine the signal of block lengths around a selected locus, by measuring the ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i+)+l_A(m_i-)}}$ of mean block lengths surrounding a site with the mean length of adjacent blocks (Figures~\ref{Supp:ratioBlockAdjacent},~\ref{Supp:ratioBlockAdjacentHeatmap})

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning}
\caption{Mean block length, $l_B(m_i)$, along a simulated chromosome of length $1M$ with selected locus at position $0.5M$. Here each line represents  $l_B(\mathbf{m})$, the mean block lengths in a given deme, and is normalized by mean block length $l_B(m_i)$ along the chromosome in the deme.}\label{Fig:blockLengths}
\end{figure}
